Covariate analysis of ROSMAP reprocessed counts (with TMM normalisation)

### 2017-01-13 code/Rmd/ROSMAP_RNASeq_Reprocessed_TMM.Rmd
Minor modifications

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix %>%
  rownameToFirstColumn('gene.id') %>%
  write.table(file = 'ROSMAP_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('ROSMAP_DLPFC_Counts.tsv', name = 'Raw counts (filtered)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                     executed = thisFile, activityDescription = activityDescription)

>>>>

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix %>%
  as.matrix() %>% rownameToFirstColumn('gene.id') %>%
  write.table(file = 'ROSMAP_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('ROSMAP_DLPFC_Counts.tsv', name = 'Raw counts (filtered)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                     executed = thisFile, activityDescription = activityDescription)
